---
title: "Basic Use of Nimrmarkdown"
author: "Luis Araujo"
date: "`r format(Sys.Date(), '%b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Basic Use of nimrmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knit_opts, include=FALSE}
knitr::opts_chunk$set(eval = nzchar(Sys.getenv("VIG")))
```

This discussion assumes you already have a basic understanding
of Markdown for document formatting, Rmarkdown to include executable
code in a document, and nim to write the code.

## First attach the `nimrmarkdown` library
Your first code chunk will look something like this:

    ```{r library}`r ''`
    library(nimrmarkdown)
    ```
    
This will either report that nim was found, or
that you need to specify it\'s location yourself.

```{r library, echo=FALSE}
library(nimrmarkdown)
```

You can hide all of this so it does not appear in your
final document by using the `echo=FALSE, message=FALSE`
chunk options.

## If nim was not found
You will need to specify this yourself, as an alternative line in
the \"library\" code block.


```{r nimexe, eval=FALSE}
nimexe <- "/home/luis/.nimble/bin/nim"
```


## Then set up nim code chunks.
A simple code chunk in Rmarkdown might look like:

    ```{nim example}`r ''`
    echo "cool, this works"
    ```

And in your document this would produce:

```{nim example}
echo "cool, this works"
```
